\documentclass[12pt]{article}
\usepackage{amsmath} 
\usepackage{esint} 
\usepackage{amsfonts} 
\usepackage{amssymb} 
\usepackage{geometry}  

\usepackage[style=numeric,backend=biber]{biblatex}
\addbibresource{references.bib}


\newcommand{\R}{\mathbb{R}}
\newcommand{\atlas}{\mathcal{A}}
\newcommand{\p}{\partial}
\newcommand{\at}[2]{\left. #1 \right|_{#2}}
\newcommand{\bv}[1]{\mathbf{#1}}
\newcommand{\uv}[1]{\hat{#1}}




\begin{document}

\title{Exterior Calculus}
\author{Daniel Pesic}
\maketitle
\newpage
\tableofcontents
\newpage
\section{Introduction from Vector Calculus}
\subsection{Vector Calculus Motive}
Vector Calculus is a powerful yet limited tool. It allows us to extend the concepts from single-variable Calculus to higher dimensional spaces, more complex functions, and different varieties of functions. However, it begins to fail when space becomes non-Euclidean or the functions we attempt to measure rise in complexity and abstraction; when we ask:
\begin{itemize}
    \item How can we analyze a function with a non-Euclidean input space?
    \item In Vector Calculus, curl is limited to vector fields in $\R^3$. How can we find the vorticity of a higher dimensional vector field?
    \item How can we analyze functions intrinsically without relying on coordinates?
\end{itemize}

The primary goal of Exterior Calculus is to provide an abstract framework with a specialized algebra to analyze complex geometric systems. It must not replace Vector Calculus, but build upon it to help us understand what lies beyond. 
\subsection{Limitations of Integral Theorems}
Consider the three integral theorems of Vector Calculus. These theorems are viewed as the capstone of the field, giving a geometric relation between the ideas of flux, vorticity, boundaries, and integrals.
\\\\ Green's Theorem
\[
\oint_{\partial D} (P\,dx + Q\,dy)
=
\iint_{D}
\left( (\vec{\nabla} \times \bv{F}) \cdot \uv{k} \right)
\, dA
\]
 Stokes' Theorem
\[
\oint_{\partial S} \bv{F} \cdot d\bv{r}
=
\iint_{S}
(\vec{\nabla} \times \bv{F}) \cdot \uv{n}
\, dS
\]
Gauss' Theorem
\[
\oiint_{\partial V}
(\bv{F} \cdot \uv{n}) \, dS
=
\iiint_{V}
(\vec{\nabla} \cdot \bv{F}) \, dV
\]
From the Vector Calculus viewpoint, these theorems each have specific use cases and seem quite different compared to each other; they are only applicable in sub-regions of $\R^3$ with specific kinds of functions. However, one might notice a pattern shared between them: the boundary integral of some function equals the integral of some form of derivative of the function. This can even be seen in the ordinary Fundamental Theorem of Calculus:

\[
f(b)-f(a) = \int_{[a,b]}{\frac{df}{dx}dx} \iff\int_{\p[a,b]}{f} =\int_{[a,b]}{\frac{df}{dx}dx}
\]

This pattern is not simply coincidental, as we will soon discover how these four theorems emerge from one overarching theorem at the top of Exterior Calculus: the Generalized Stokes' Theorem. 

\subsection{Roadmap}
Exterior Calculus provides a unified framework that expands the concepts of Vector Calculus through extension, generalization, and unification.
\subsubsection{Extension}
Vector Calculus handles derivatives and integrals on $\R^3$. Exterior Calculus extends these concepts to arbitrary dimensions spaces known as manifolds that are locally Euclidean but have complex global behavior. 
\subsubsection{Generalization}
The derivative in Exterior Calculus, the exterior derivative, generalizes gradient, curl, and divergence into one operator. Similarly, integration over manifolds generalizes line, surface, and volume integrals in a dimension-independent manner. 
\subsubsection{Unification}
Exterior Calculus unifies Green's, Stokes', and Gauss's theorems, along with the Fundamental Theorem of Calculus into one abstract theorem: the Generalized Stokes Theorem.

These functions of Exterior Calculus are precisely what make it such a powerful framework. Throughout this paper, we will begin at the level of Vector Calculus and build up through these extensions, generalizations, and unifications to show the full theory of Exterior Calculus along with its geometric and physical applications.


\section{Manifolds}

A manifold is an $n$-dimensional structure that is locally homeomorphic to $\R^n$. This essentially means that a manifold can be split into a number of regions that can each be mapped to a region of $\R^n$ in a way that preserves its local topological structure. For example, each hemisphere of the sphere $S^2$ can be mapped to $\R^2$ and mapped back while preserving the structure.

Manifolds are important to Exterior Calculus as they serve as the generalization of space. A scalar function $f$ can exist on a manifold $M$ by $f:M\to \R$. This is an example of extension from Vector Calculus: $\R^n$ is also a manifold and thus a function input space, but non-Euclidean input spaces can be used in addition. In Vector Calculus, we perform calculus on smooth functions. For Exterior Calculus, we need a smooth function defined on a smooth manifold. We will now look into the mathematical construction behind smooth manifolds.

\subsection{Constructing Smooth Manifolds}

\subsubsection{Topological Manifolds}
A manifold is, at its core, a space that looks locally like ordinary Euclidean space. A topological manifold ensures this resemblance at the level of continuity, while a smooth manifold strengthens this resemblance so that calculus can be performed consistently.

In Exterior Calculus, we require the smooth structure so that differentiation is globally well defined. The full technical construction of smooth manifolds is provided in APPENDIX.

\subsubsection{Coordinate Charts}
The core parts of a manifold that define its geometric relation to Euclidean space are the coordinate charts. These are precisely what defines the locally Euclidean characteristic of manifolds, which gives the basis for analysis. 

Around every point in $M$, there exists a neighborhood $U$ that can be assigned coordinates $(x^1,x^2, \dots, x^n)$ just like a region of $\R^n$. These coordinates give a way to label points in the neighborhood and map them to $\R^n$ while preserving the geometric structure. The coordinate functions $x^i:U\to \R$ give a method of labeling points in the neighborhood; however, it is an important distinction that coordinates are not directly connected to the geometric structure of the manifold. This will be covered in Section 3. 

However, coordinate charts alone are not enough to describe the full differentiable structure of a manifold. They do not let us understand the structure of differentiability that lies between the charts.

\subsubsection{Transition Maps}
When two coordinate neighborhoods overlap, there must be a way to translate coordinates from one chart to the other. These coordinate translations are called transition maps. They ensure that the transition between the two charts is fully smooth by creating a map that retains the geometric information from the charts. If this mapping is smooth, it ensures that derivatives in one chart correspond to derivatives in the other. This allows smoothness to become an intrinsic property of the manifold rather than depending on a chart.


\subsubsection{Atlases}
An atlas $\atlas$ is defined as a collection of charts on $M$ that cover the entire manifold. When every possible coordinate chart has a smooth transition map with every other chart, the atlas creates a smooth structure on the space. This is called a maximal smooth atlas, and it describes the structure of the entire manifold.

\subsubsection{Smooth Manifolds}

A smooth manifold $M$ is defined as a set of points combined with a maximal smooth atlas $\atlas$. Since smooth manifolds are ubiquitous in Exterior Calculus, we will simply use the term "manifold" to refer to one. With this definition, we can extend the idea of space to include all manifolds rather than solely $\R^n$. By defining a smooth manifold, smooth functions can be defined beyond $\R^n$ and behave well under analysis. However, this generalization raises more questions than it answers. If manifolds only resemble Euclidean space locally, how can we define derivatives in a way that does not depend on a particular coordinate system?

\subsection{Tangent Vectors as Derivations}
In Vector Calculus, the directional derivative finds the derivative of a scalar function on a particular vector. In Exterior Calculus, we can define abstract vectors (that is, vectors not defined in coordinates) that are tangent to a manifold and act as a derivative operator, a derivation.
\subsubsection{Local Coordinate Vector Fields}
In $\R^n$, the global coordinates induce a global coordinate vector field. For example, in $\R^3$, the coordinates $(x,y,z)$ induce $\uv{i}, \uv{j}, \uv{k}$.

Since a smooth manifold does not have a global coordinate chart, the coordinate vector fields must be expressed locally. Take a point $p$. The coordinate chart
\[
(U,\varphi), \quad \varphi = (x^1,x^2, \dots, x^n), \quad p\in U
\]
induces the local coordinate vector fields $\frac{\p}{\p x^1}, \frac{\p}{\p x^2},\dots \frac{\p}{\p x^n}$ on $U$. These vectors point in the direction of their corresponding coordinate. This notation of expressing coordinate vectors as partial derivative operators will be explained in Section 2.2.3. For now, treat it purely as notation.
\subsubsection{Tangent Vectors}
A tangent vector on a manifold is a vector attached at a specific point $p$ such that it is tangent to the surface of the manifold. In coordinates, a tangent vector is a linear combination of the local coordinate vector fields. However, we will define a more geometric definition for abstract tangent vectors that does not rely on an arbitrary coordinate chart.

Choose a smooth parametric curve on an embedded manifold $\gamma:I \subseteq \R \to M$ such that $\gamma(0)=p$. A vector $v$ is a tangent vector at $p$ iff $\dot{\gamma}(0) = v$. An important distinction is that the derivative of a curve on a manifold is only predefined when the manifold can be embedded in $\R^n$. We can choose a more abstract definition using derivations. 

\subsubsection{Derivations}
A derivation is a differential operator that computes directional derivatives along an abstract tangent vector. The tangent vector is not an input to a derivation, but the operator itself. Specifically, a tangent vector is a derivation $v:C^{\infty}{(M)} \to \R$.

For an operator to be a derivation, it must satisfy these two axioms:
\begin{enumerate}
    \item Linearity: $\forall f,g \in C^{\infty}(M)$ and $c,d \in \R, \quad v(cf + dg) = cv(f)+dv(g)$
    \item Leibniz Rule: $v(fg) =fv(g)+gv(f)$
\end{enumerate}
In coordinates, the tangent vector becomes a linear combination of local coordinate vectors:
\[
v^i\frac{\p}{\p x^i}
\]
The numerical value of the derivation applied to a function is:
\[
v^i\at{\frac{\p f}{\p x^i}}{p} 
\]
Another way to represent the derivation on a function is through the abstract definition with parametric curves:
\[
v(f)=\frac{d}{dt}\at{f(\gamma(t))}{t=0}
\]
This generalization through tangent vectors gives us an abstract way to represent directional derivatives on manifolds and serves as a crucial stepping stone towards higher level concepts.
\subsubsection{More on the Leibniz Rule}
The Leibniz rule $v(fg)=fv(g)+gv(f)$ is a minimal equation that encodes differential properties into a functional. It creates a derivation by satisfying these axioms of differentiation:
\begin{enumerate}
    \item The derivative of a constant must be 0
    \item Derivatives must only extract first order change
\end{enumerate}

When a constant is plugged into a derivation, the Leibniz rule forces:
\[
v(1\cdot1) = 1\cdot v(1)+1\cdot v(1) \implies v(1)=2v(1) \implies v(1)=0
\]
\[
\forall c\in\R, v(c)=v(\sum_{c}{1}) = \sum_{c}{v(1)} = \sum_{c}{0} = 0
\]
Additionally, the Leibniz rule forces derivations to extract solely first order change. Consider the product rule of differentiation for functions in $\R^n$, the specific case of the Leibniz rule in Euclidean space:
\[
\frac{d}{dx^n}\left[fg\right] =f\frac{dg}{dx^n}+g\frac{df}{dx^n}
\]
If both $f$ and $g$ are 0 at a point $p$, the derivative in every direction must be 0. Regardless of higher order change and curvature, the function $fg$ must have no first order change, ensuring that the derivation measures only the instantaneous change of a function at a point. This property is retained when generalizing to manifolds, which enforces the idea how the Leibniz rule forces derivations to satisfy the axioms of differentiation.

\subsection{Tangent Spaces and Bundles}

 While tangent vectors are useful as derivations, we can group them into ordered structures to help us better understand a manifold.

\subsubsection{Tangent Spaces}
The set of all tangent vectors at a point $p$ is called the tangent space $T_pM$. Since, in coordinates, every tangent vector at a point is a linear combination of its local coordinate vectors $\frac{\p}{\p x^1},\frac{\p}{\p x^2}...\frac{\p}{\p x^n} $, the local coordinate vectors form a basis for $T_pM$ with respect to a local chart. Every tangent vector $v$ at $p$ satisfies $v \in T_pM$. 

On an $n$-manifold, $T_pM$ is an $n$-dimensional vector space analogous to $\R^n$

\subsubsection{Tangent Bundles}
The tangent bundle $TM$ is the set of all tangent vectors on a manifold. It is defined by: \[
TM :=\bigsqcup_{p\in M}{T_pM}
\]
The disjoint union forces each vector to be paired with its origin point. Thus, it can also be defined as:
\[
TM := \bigcup_{p\in M}{\{p\} \times T_pM}
\]
Therefore, each element of $TM$ takes the form $(p,v)$. This allows us to create a projection map:
\[
\pi:TM \to M \quad(p,v) \mapsto p
\]
A tangent vector fiber over a point $p$ in $M$ is $\pi^{-1}(p)$, which gives $T_pM$. This allows us to create global mappings and assignments over the manifold.
\subsubsection{Vector Fields}
A vector field, that is, a section of the tangent bundle, assigns a tangent vector to each point on a manifold: 
\[
\bv{X}:M\to TM
\]
It must satisfy $\pi \circ \bv{X} = \text{id}_M$, where $\text{id}_M$ is the identity map on the manifold. Intuitively, this ensures that vectors are assigned correctly.
At a point, the vector field satisfies $\bv{X}(p)= v\in T_pM$. Defining the tangent bundle and projection map helps us create a simple definition for tangent vector fields on a manifold.

\subsection{Submanifolds and Boundaries}
The final parts of manifolds we must mention are submanifolds and boundaries. These are imperative to define future notions of integration.

\subsubsection{Submanifolds}

Given two manifolds $M$ and $N$, $M$ is a submanifold of $N$ iff $M \subseteq N$. For example, the sphere $S^2$ is a submanifold of $\R^3$ as $S^2 \subset \R^3$. Submanifolds give us a generalized way to define regions for integration. For example, the region $[0,1] \times [0,1]$ can be expressed as a submanifold of $\R^2$. 

There are also two more structured types of submanifolds: immersions and embeddings. 

An immersion is a smooth map between manifolds $f:M \to N$ such that the image $f(M) \subseteq N$ is locally injective. Because the image of the immersion $f(M)$ is not globally injective, it may intersect itself, and its topology may not match $M$. For example, $M = (0,2\pi)$ can be immersed in $\R^2$ through $f:M \to \R^2, \quad f(t) \mapsto (\cos(t),\sin(t))$ as a circle missing one point. $0$ and $2\pi$ are distant from each other in $M$, but they become infinitely close in $f(M)$. Therefore, sequences that diverge in $M$ can converge in $f(M)$, so they are not topologically equivalent.

An embedding is an immersion $f:M \to N$ such that $f$ is globally injective and $f(M) \subseteq N$ is homeomorphic to $M$. Due to these properties, $f(M)$ cannot intersect itself and is topologically equivalent to $M$. 

Another important remark about immersions and embeddings is their connection with the Whitney immersion theorem and the strong Whitney embedding theorem. The Whitney immersion theorem states that any smooth $n$-dimensional manifold can be immersed in $\R^{2n-1}$, while the strong Whitney embedding theorem says that any smooth $n$-dimensional manifold can be embedded in $\R^{2n}$. An excellent example of this is the Klein bottle, a 2-manifold. The Klein bottle can exist in $\R^3$ as an immersion, however, it must intersect itself to stay closed. It can only be embedded in $\R^4$ where it stays closed without intersection.


\subsubsection{Boundaries}

In simplest terms, the boundary of a smooth $n$-manifold $M$ is a smooth $(n-1)$-manifold $\p M$ embedded as its boundary points. In this case, $M$ is a manifold with boundary while $\p M$ is a manifold without boundary. The notation $\p M$ solely refers to the boundary of M and has no connection to partial derivatives. In essence, the boundary of a manifold is the set of points on the manifold that are not in the interior. 

Boundary manifolds are deeply connected to boundary integrals $\oint$, as they create the region that is integrated over. By defining boundary manifolds, we generalize boundary integration to manifolds, which is crucial when we discuss integration.

\section{Coordinate Invariance}

Coordinates are used frequently in fields such as vector calculus to describe and quantify change. However, there are infinitely many coordinate systems that can be used to describe a structure such as a vector space or manifold. Coordinate invariance dictates that a certain object encodes the same geometric properties regardless of the coordinate system used to describe it. For example, $(1, 1)$ in Cartesian coordinates represents the same geometric vector as $( \sqrt{2}, \frac{\pi}{2} )$ in polar coordinates.

\subsection{Coordinates as Convenience}

Coordinates are incredibly useful for deriving quantitative information from a geometric system. However, they do not constitute the geometry itself. A sphere, such as the Earth, has intrinsic properties such as distance and curvature. Latitude and longitude are one system used to describe these properties, but spherical coordinates, Cartesian coordinates, or any other smooth coordinate chart can be used to describe them. Regardless of which label is chosen to represent a point or a path, the Earth remains unchanged. Therefore, distance and curvature are coordinate invariant, which is precisely what makes them geometric properties.

This does not mean that coordinates are meaningless, however. They are auxiliary tools used to describe a geometric system, which make them useful .

\subsection{Tensorial Objects Under Coordinate Change}

When coordinates are changed, the numerical components used to describe a geometric object will generally change as well. However, if the object is truly geometric, this change in components must occur in a way that preserves the underlying object itself. This requirement leads to the tensor transformation law.

\subsubsection{Tensor Transformations}

Let $(x^1, \dots, x^n)$ and $(x^{1'}, \dots, x^{n'})$ be two coordinate systems on the same region of a manifold. A vector can be expressed in either coordinate system as
\[
V = V^{i}\frac{\p}{\p x^i} = V^{i'}\frac{\p}{\p x^{i'}}
\]
where $\frac{\p}{\p x^i}$ and $\frac{\p}{\p x^{i'}}$ are local coordinate vector fields. These coordinate vectors are related by the chain rule
\[
\frac{\p}{\p x^j} = \frac{\p x^{i'}}{\p x^j}\frac{\p}{\p x^{i'}}
\]
which gives the Jacobian as the core tool to change coordinates. A conceptual way to consider this is that the tangent basis vectors encode first order behavior as shown in Section 2.2.4. Therefore, the Jacobian, a linear map, contains all of the information needed for the vectors to transform, even if the coordinate change is nonlinear. This transformation ensures that the vector itself remains unchanged, even though its numerical description differs. Objects whose components transform according to this type of rule are called tensors, which include scalars, vectors and more. These objects and their properties will be covered in more detail in Section 4.1, along with their generalized transformation law.

\subsubsection{Coordinate Dependent Objects}

A coordinate dependent object is an artifact from the given coordinate system and does not represent the geometry of the overall space. For example, consider the second partial derivative of a function with respect to a particular coordinate. By the chain rule, the first derivative transforms as

\[
\frac{\p f}{\p x^{i'}}
=
\frac{\p x^k}{\p x^{i'}}
\frac{\p f}{\p x^k}.
\]

Taking another derivative, we obtain

\[
\frac{\p}{\p x^{j'}} \left( \frac{\p f}{\p x^{i'}} \right) = \frac{\p}{\p x^{j'}} \left(
\frac{\p x^k}{\p x^{i'}}
\frac{\p f}{\p x^k} \right).
\]

When evaluated with the product rule, we obtain
\[
\frac{\p^2 f}
{\p x^{i'} \p x^{j'}}
=
\frac{\p x^k}{\p x^{i'}}
\frac{\p x^l}{\p x^{j'}}
\frac{\p^2 f}{\p x^k \p x^l}
+
\frac{\p^2 x^k}
{\p x^{i'} \p x^{j'}}
\frac{\p f}{\p x^k}
\]

This result does not obey the tensor transformation law, and contains a coordinate artifact. This means that second partial derivatives, by themselves, do not define intrinsic geometric objects. The underlying issue is that the partial derivative operator
\[
\frac{\p}{\p x^i}
\]
	
is tied to the particular coordinate system $x^i$. When the coordinates change, these operators change in a way that reflects the coordinate grid rather than the intrinsic geometry. This is why the second partial derivative is not intrinsically geometric, as it combines the function's intrinsic curvature with the curvature of the coordinate grid.

\subsubsection{Geometric Meaning of the Tensor Transformation Law}

The tensor transformation law provides the precise criterion for distinguishing intrinsic geometric objects from coordinate artifacts. If an object's components transform according to the tensor law, the object exists independently of coordinates and represents an intrinsic geometric quantity. If not, the object depends on the coordinate system and does not represent intrinsic geometry. In this way, tensors form the natural basis of coordinate invariant geometry.

\subsection{The Guiding Principle of Coordinate Invariance}

By prioritizing our analysis on coordinate independent objects, we create a generalized system that allows us to describe the geometry of any given objects without relying on coordinates. While coordinates can be very useful for describing some phenomena, every definition will be given in a coordinate independent manner. This allows us to consider the underlying geometry, which becomes incredibly important as concepts progress. 

\section{Differential Forms}

One primary goal of Exterior Calculus is to create a generalized object that can be integrated and differentiated. A more detailed way to describe this object would be:

\begin{enumerate}

\item When evaluated at a point on $M$, a derivation $v$ will act on this object to produce a scalar value corresponding to both of their properties
\item When evaluated on a parametrization $\gamma$ on $M$, it returns a scalar value based on each tangent vector that may be summed
\end{enumerate}

For now, let us refer to this object as $\omega$. In other words,
\[
\omega (v) \to \R
\]

\[
\omega(\gamma(p)) \to \R \implies \int_{\gamma}{\omega} \to \R
\]

This gives a very simple notion of differentiation and integration on manifolds. However, to truly capture these concepts, $\omega$ must encode a deep, geometric way to analyze change, accumulation, and orientation. This is the primary goal of this text: to explain how $\omega$ is developed into an object that encapsulates the concepts from Vector Calculus while generalizing them in an abstract way.

\subsection{Multilinear Maps and Tensors}

\subsubsection{Multilinear Maps}

Recall the definition for a linear map between vector spaces $T: V \to W$

\[
T(au + bv) = aT(v)+bT(u) \quad a,b \in \R, \; u,v \in V.
\]

A multilinear map is a map 
\[
T: V_1 \times \dots \times V_n \to W
\]

that is linear with respect to each variable. That is, for each variable $u$ in $T$, if all other variables are held constant, $T$ is linear in $u$. For example, the dot product in $\R^n$ is multilinear (specifically, bilinear), as
\[
(au + bv) \cdot w = a(u \cdot w) + b(v \cdot w) \text{ and } u \cdot (av + bw) = a(u \cdot v) + b(u \cdot w).
\]

Multilinear maps are a crucial concept as they allow us to define tensors, which is the fundamental concept that $\omega$ is built upon.

\subsubsection{Covectors}

Before discussing tensors, we must mention covectors. Given a vector space $V$, its dual space $V^*$ is the set of all linear mappings 
\[
c: V \to \R.
\]
Each element $c$ is a covector. 

This formal definition of a covectors is helpful as they are used extensively. For example, the inner product of two vectors represented as $v^T u$ simply means
\[
v^T u = \text{the dual of }v \text{ (}v^T\text{) applied to u," which results in a scalar value.}
\]

Therefore, a covector is simply an object that linearly maps a vector to a real number.

\subsubsection{Tensors}
A tensor is a specific type of multilinear map that maps covectors and vectors to a scalar value.
\[
T: V^*_1 \times \dots \times V^*_p \times V_1 \times \dots \times V_q \to \R.
\]

This is specifically referred to as a type $(p,q)$ tensor.

For example, a covector is a $(0,1)$ tensor via
\[
T: V_1 \to \R.
\]
A vector is a $(1,0)$ tensor
\[
T: V^*_1 \to \R.
\]
The dot product is a $(0,2)$ tensor
\[
T:V_1 \times V_2 \to \R.
\]
All of these geometric objects have a representation as a multilinear map. This is the abstract form of a tensor. The coordinate representation can be obtained by applying the tensor to basis elements. For example, the dot product of vectors $x$ and $y$ with basis ${e_1, e_2}$ can be represented by
\[
T(x_1 e_1+x_2 e_2, y_1 e_1+y_2 e_2).
\]
This can be expressed as a matrix
\[
\begin{bmatrix} 
T(e_1, e_1), T(e_1, e_2) \\
T(e_2, e_1), T(e_1, e_2)
\end{bmatrix}.
\]
Therefore, the dot product can be expressed as
\[
\begin{pmatrix}
x_1 & x_2
\end{pmatrix}
\begin{pmatrix}
1 & 0 \\
0 & 1
\end{pmatrix}
\begin{pmatrix}
y_1 \\
y_2
\end{pmatrix}
\]


\section {Citations}
\nocite{*}
\printbibliography

\end{document}

